scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Wording fixes

Visualizing images is an important component of the image processing
workflow, in order to verify the final result and to adjust the
parameters of intermediate processing operations.
\texttt{matplotlib}~\citep{Hunter2007} is the most popular 2D plotting
library of the Python ecosystem. It can be used to visualize 2D data such
as color or grayscale images, and 1D data such as contour lines, outlines
of segmented regions, histograms of gray levels, etc. Although
\texttt{matplotlib} has simple 3D plotting capabilities, it is
recommended to use the \texttt{mayavi} module~\citep{Ramachandran2011}
for applications requiring advanced 3D visualization, such as tomography. 
\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
visualizing data passed as \texttt{numpy} arrays. For more advanced
visualizations, a large majority of VTK capabilities can be accessed
thanks to a pipeline API. A visualization pipeline can be designed either
using the pipeline API, or graphically in the pipeline window.
\texttt{mayavi} offers a good trade-off between simplicity of use for
common operations, and more advanced possibilities, including responsive
visualizations.

>>>>

Visualizing images is an important component of the image processing
workflow, in order to verify the final result and to adjust the
parameters of intermediate processing operations.
\texttt{matplotlib}~\citep{Hunter2007} is the most popular 2D plotting
library of the Python ecosystem. It can be used to visualize 2D data such
as color or grayscale images, and 1D data such as contour lines, outlines
of segmented regions, histograms of gray levels, etc. Although
\texttt{matplotlib} has simple 3D plotting capabilities, we
recommend using the \texttt{mayavi} module~\citep{Ramachandran2011}
for applications requiring advanced 3D visualization, such as tomography. 
\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
visualizing data passed as \texttt{numpy} arrays. For more advanced
visualizations, a large majority of VTK capabilities can be accessed
thanks to a pipeline API.
\texttt{mayavi} offers a good trade-off between simplicity of use for
common operations, and more advanced possibilities, including responsive
visualizations.
